---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# blueycolors

<!-- badges: start -->
<!-- badges: end -->

blueycolors provides color palettes and ggplot2 `color` and `fill` scales inspired by [Bluey](https://www.bluey.tv/)

## Installation

You can install blueycolors from Github via:

``` r
devtools::install_github("ekholme/blueycolors")
```

## Usage

There are probably 2 main uses for this package:

1. Extracting palettes and their associated hex codes
2. Using these palettes as color or fill aesthetics in ggplot

To extract palettes & hex codes, use the `bluey_palette()` function:

```{r}
library(blueycolors)

bluey_palette("bluey")
```

To use the palettes in ggplot, use `scale_color_bluey()` and `scale_fill_bluey()` for discrete scales or `scale_color_bluey_c()` and `scale_fill_bluey_c()` for continuous scales.

```{r}
library(ggplot2)

tmp <- data.frame(
  x = rnorm(100),
  y = rnorm(100),
  z = rep(c("a", "b", "c", "d"), 25)
)

ggplot(tmp, aes(x = x, y = y, color = z)) +
  geom_point() +
  scale_color_bluey()
```

```{r}
tmp2 <- data.frame(
  x = 1:5,
  y = c("a", "b", "c", "d", "e")
) 

ggplot(tmp2, aes(x = x, y = y, fill = y)) +
  geom_col() +
  scale_fill_bluey(option = "socks")
```

There are currently [4 different palettes available](#palettes), but the "heeler" option probably provides the best contrast. 

## Palettes

Bluey (default)

```{r}
library(scales)

show_col(bluey_palette("bluey"))
```

Chilli

```{r}
show_col(bluey_palette("chilli"))
```

Heeler

```{r}
show_col(bluey_palette("heeler"))
```

Socks

```{r}
show_col(bluey_palette("socks"))
```
